\documentclass[10.5pt,]{article}

\usepackage{multicol} % for multiple columns



\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\else % if luatex or xelatex
\ifxetex
\usepackage{xltxtra,xunicode} %originally, \usepackage{mathspec}. This change is to produce Chinese
\else
\usepackage{fontspec}
\fi
\defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
	\usepackage{microtype}
	\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}


% Make lists without bullets
\renewenvironment{itemize}{
	\begin{list}{}{
			\setlength{\leftmargin}{1.5em}
		}
	}{
	\end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}

\usepackage{ctex}
% Siyuan Font
%\setCJKmainfont[BoldFont = Noto Sans CJK SC]{Noto Serif CJK SC}
%\setCJKsansfont{Noto Sans CJK SC}
%\setCJKfamilyfont{zhsong}{Noto Serif CJK SC}
%\setCJKfamilyfont{zhhei}{Noto Sans CJK SC}
%\setCJKfamilyfont{zhkai}{simkai.ttf}

% less space for the Chinese format
\titlespacing\section{0pt}{1pt plus 4pt minus 2pt}{1pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{5pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}


% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}
\newfontfamily\FA{FontAwesome.otf} % Explicitly provide .otf

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
	\cfoot{\scriptsize  Yuehong Cassandra Tai - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
		pdftitle={Yuehong Cassandra Tai:  CV (Curriculum Vitae)},
			pdfauthor={Yuehong Cassandra Tai},
			colorlinks=true,
	linkcolor=blue,
	citecolor=Blue,
	urlcolor=blue,
	breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% try to fit picture


\begin{document}
	
	
	\centerline{\huge \bf Yuehong Cassandra Tai}
	
	
	
	\vspace{2 mm}
	
	\hrule
	
	\vspace{2 mm}
	
	
	
	\moveleft.5\hoffset\centerline{ {\FA\faEnvelope} \hspace{1 mm} \href{mailto:}{\tt \href{mailto:yhcasstai@psu.edu}{\nolinkurl{yhcasstai@psu.edu}}} \hspace{1 mm}     {\FA\faGlobe} \hspace{1 mm} \href{http://cassyuehtai.netlify.app}{\tt cassyuehtai.netlify.app}   }
	
	\vspace{2 mm}
	
	\hrule
	
		
	\section{ACADEMIC APPOINTMENTS}\label{academic-appointments}

\begin{itemize}
\tightlist
\item
  Pennsylvania State University

  \begin{itemize}
  \tightlist
  \item
    Assistant Research Professor, Center for Social Data Analytics
    \hfill 2025-
  \item
    Assistant Director, Center for Social Data Analytics
  \item
    Postdoctoral Scholar, Center for Social Data Analytics
    \hfill 2022-2024
  \end{itemize}
\end{itemize}

\section{EDUCATION}\label{education}

\begin{itemize}
\tightlist
\item
  \textbf{Ph.D.} Program in Political Science, University of Iowa,
  U.S.A. \hfill 2017-2022

  \begin{itemize}
  \tightlist
  \item
    Fields: Comparative Politics, Political Methodology, American
    Politics
  \end{itemize}
\item
  \textbf{MSc} in International Political Economy, Nanyang Technological
  University, Singapore \hfill 2008
\item
  \textbf{LL.B.} in Diplomacy, Renmin University of China, China
  \hfill 2007
\end{itemize}

\section{RESEARCH AREAS}\label{research-areas}

\begin{itemize}
\tightlist
\item
  \textbf{AI in Social Science}

  \begin{itemize}
  \tightlist
  \item
    Generative AI Evaluation, AI-Assisted Measurement, Human-AI
    Collaboration, Research Transparency and Reproducibility.
  \end{itemize}
\item
  \textbf{Political Science}

  \begin{itemize}
  \tightlist
  \item
    AI and Democratic Accountability, Political Communication, Public
    Opinion.
  \end{itemize}
\end{itemize}

\section{PUBLICATIONS}\label{publications}

\begin{itemize}
\tightlist
\item
  \textbf{AI and Computational Social Science}

  \begin{itemize}
  \tightlist
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{16}
    \tightlist
    \item
      \textbf{Tai, Yuehong Cassandra}, Yu-Ru Lin, and Bruce A.
      Desmarais. 2026. ``Public Oﬀicials' Online Sharing of
      Misinformation: Institutional and Ideological Checks.''
      \emph{Political Communication}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{15}
    \tightlist
    \item
      Yu, Dong Erico, and \textbf{Yuehong Cassandra Tai}. 2026. ``Speak
      `As Good As Men'? An Empirical Study of Gender Variation in
      Chinese Courtroom Audio'' \emph{Accepted at Political Studies
      Review}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{14}
    \tightlist
    \item
      \textbf{Tai, Yuehong Cassandra}, Nitheesha Nakka, Khushi Navin
      Patni, Sarah Rajtmajer, Kevin Munger, Yu-Ru Lin, and Bruce A.
      Desmarais. 2025. ``The Digitally Accountable Public Representation
      Database: Measuring Online Communication by Federal, State, and
      Local Oﬀicials.'' \emph{Nature Scientific Data}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{13}
    \tightlist
    \item
      \textbf{Tai, Yuehong Cassandra}, Khushi Navin Patni, Nicholas
      Daniel Hemauer, Bruce A. Desmarais, and Yu-Ru Lin. 2025. ``GenAI
      vs.~Human Fact-Checkers: Accurate Ratings, Flawed Rationales.'' In
      \emph{Proceedings of the 17th ACM Web Science Conference 2025}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{12}
    \tightlist
    \item
      Nakka, Nitheesha, Issac Pollert, Lingyu Fuca, and \textbf{Yuehong
      Cassandra Tai}. 2025. ``Navigating Hate and Anti-Hate Speech:
      Bridging Large Language Model and Human Expertise in Public
      Oﬀicials' Online Communication.'' {[}\textbf{with graduate
      students}{]} \emph{Workshop Proceedings of the 19th International
      AAAI Conference on Web and Social Media.}
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{11}
    \tightlist
    \item
      Biswas, Ahana, Yu-Ru Lin, \textbf{Yuehong Cassandra Tai} and Bruce
      A. Desmarais. 2025. ``Political Elites in the Attention Economy:
      Visibility Over Civility and Credibility?'' In \emph{Proceedings
      of the International AAAI Conference on Web and Social Media.}
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{10}
    \tightlist
    \item
      \textbf{Tai, Yuehong Cassandra}, Roan Buma and Bruce A. Desmarais.
      2023. ``Oﬀicial Yet Questionable: Examining Misinformation in U.S.
      State Legislators' Tweets.'' \emph{Journal of Information
      Technology \& Politics}.
    \end{enumerate}
  \end{itemize}
\item
  \textbf{Public Opinion and Measurement}

  \begin{itemize}
  \tightlist
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{9}
    \tightlist
    \item
      \textbf{Tai, Yuehong Cassandra} and Frederick Solt. 2026. ``Trust
      in Civil Servants: A Cross-National Dataset for Public Policy
      Research, 1986--2022'' \emph{Accepted at Political Studies}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{8}
    \tightlist
    \item
      Hu, Yue, \textbf{Yuehong Cassandra Tai}, and Frederick Solt. 2026.
      ``Data Wrangling Before Harmonization: Best Practices for Getting
      Past the `Janitor Work.'\,'' \emph{Accepted at PS: Political
      Science \& Politics}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{7}
    \tightlist
    \item
      \textbf{Tai, Yuehong Cassandra}. 2026. ``Introducing the Trust in
      Government (TrustGov) Dataset: A New Resource for Cross-National
      Time-Series Trust Research'' \emph{Research \& Politics}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{6}
    \tightlist
    \item
      \textbf{Tai, Yuehong Cassandra}. 2025. ``The Upsides and Downsides
      of Generalized Trust: The Mediating Effect of Democratic
      Institutions.'' \emph{International Journal of Public Opinion
      Research}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{5}
    \tightlist
    \item
      Hu, Yue, \textbf{Yuehong Cassandra Tai}, Hyein Ko, Byung-Deuk Woo,
      and Frederick Solt. 2025. ``An Incomplete Recipe: One-Dimensional
      Latent Variables Do Not Capture the Full Flavor of Democratic
      Support.'' \emph{Research \& Politics}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{4}
    \tightlist
    \item
      Woo, Byung-Deuk, Hyein Ko, \textbf{Yuehong Cassandra Tai}, Yue Hu,
      and Frederick Solt. 2024. ``Public Support for Gay Rights Across
      Countries and Over Time.'' \emph{Social Science Quarterly}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{3}
    \tightlist
    \item
      Hu, Yue, \textbf{Yuehong Cassandra Tai}*, and Frederick Solt.
      2024. ``Revisiting the Evidence on Thermostatic Response to
      Democratic Change: Degrees of Democratic Support or Researcher
      Degrees of Freedom?'' \emph{Political Science Research and
      Methods}. {[}* \textbf{co-first author}{]}
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{2}
    \tightlist
    \item
      \textbf{Tai, Yuehong Cassandra}, Yue Hu, and Frederick Solt. 2022.
      ``Democracy, Public Support, and Measurement Uncertainty''
      \emph{American Political Science Review}.
    \end{enumerate}
  \end{itemize}
\item
  \textbf{Chinese Politics}

  \begin{itemize}
  \tightlist
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{1}
    \tightlist
    \item
      \textbf{Tai, Yuehong Cassandra}, Jielu Yao and Elise Pizzi. 2022.
      ``Policy Adoption and Diffusion during the COVID-19 Crisis''
      \emph{Journal of Asian Public Policy}.
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \tightlist
    \item
      \textbf{Tai, Yuehong Cassandra}. 2022. ``Determinants of Chinese
      Provinces' Responses to the 2018 Vaccine Scandal: Policy
      Orientation and Neighboring Effect'' \emph{Asian Survey}.
    \end{enumerate}
  \end{itemize}
\end{itemize}

\section{GRANTS}\label{grants}

\begin{itemize}
\tightlist
\item
  Center for Socially Responsible Artificial Intelligence, ``Transparent
  and Reproducible AI-assisted Annotation for Social Data: A Multi-Agent
  framework,'' effective Dec 20, 2025 and expires June 30, 2027. Co-PI,
  Qunhua Li. \$25,000.
\end{itemize}

\section{WORKING PAPERS}\label{working-papers}

\begin{itemize}
\tightlist
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{2}
  \tightlist
  \item
    Ko, Hyein, \textbf{Yuehong Cassandra Tai}, and Nora Webb Williams
    ``From Annotation to Oversight: A Pipeline Approach to GenAI
    Evaluation'' {[}\textbf{Co--lead Author}{]} {[}\textbf{Under
    Review}{]}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{1}
  \tightlist
  \item
    \textbf{Tai, Yuehong Cassandra}, Xun Cao, Yu-Ru Lin, and Bruce A.
    Desmarais. ``Where Legislators Speak Changes What They Say: Platform
    Conditions Climate Attention and Framing'' {[}\textbf{Under
    Review}{]}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    Ma, Haofeng, Jeongho Choi, \textbf{Yuehong Cassandra Tai}, Yue Hu,
    and Frederick Solt. ``Macrodiscontent Across Countries''
    {[}\textbf{Revised \& Resubmitted}{]}
  \end{enumerate}
\end{itemize}

\section{WORKS IN PROGRESS}\label{works-in-progress}

\begin{itemize}
\tightlist
\item
  \textbf{AI and Computational Social Science}

  \begin{itemize}
  \tightlist
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{5}
    \tightlist
    \item
      ``Traceable Codebook-Grounded Annotation with Large Language
      Models'' (Qunhua Li)
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{4}
    \tightlist
    \item
      ``Who Speaks for AI? Local News Papers and AI Policy News Frames''
      (with Hyein Ko)
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{3}
    \tightlist
    \item
      ``Understanding Asian Hate in State Legislatures: An Electoral
      Connection'' (with Issac Michael Pollert, Nitheesha Nakka, and
      Lingyu Jack Fuca) {[}\textbf{Lead Author}{]}
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{2}
    \tightlist
    \item
      ``Large Language Models in Social Science: A Literature Review of
      LLMs and GenAI in Political Science and Communication'' (with
      Pooja Iyer)
    \end{enumerate}
  \end{itemize}
\item
  \textbf{Public Opinion}

  \begin{itemize}
  \tightlist
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \setcounter{enumi}{1}
    \tightlist
    \item
      ``How Does Public Opinion Affect Climate Change Policies?'' (with
      Xun Cao and Fred Solt) {[}\textbf{Lead Author}{]}
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{\arabic{enumi}.}
    \tightlist
    \item
      ``Surfing Waves or Making Waves? Declining Trust in Democracy and
      Election of Personalist Leaders'' (with Jia Li and M. Rosemary
      Pang)
    \end{enumerate}
  \end{itemize}
\end{itemize}

\section{CONFERENCE PRESENTATIONS}\label{conference-presentations}

\begin{itemize}
\tightlist
\item
  ``Who Speaks for AI? Local News Papers and AI Policy News Frames''

  \begin{itemize}
  \tightlist
  \item
    Midwest Political Science Association Conference \hfill April 2026
  \end{itemize}
\item
  ``From Annotation to Oversight: A Pipeline Approach to GenAI
  Evaluation''

  \begin{itemize}
  \tightlist
  \item
    Southern Political Science Association Conference \hfill Jan 2026
  \end{itemize}
\item
  ``Who Speaks, Who Falls Silent: Strategic Climate Messaging by State
  Legislators on Facebook and X''

  \begin{itemize}
  \tightlist
  \item
    Protecting the Election: AI \& Governance, Washington University in
    St.Louis, MO \hfill  Oct 2025
  \end{itemize}
\item
  ``Who Speaks, Who Falls Silent: Strategic Climate Messaging by State
  Legislators on Facebook and X''

  \begin{itemize}
  \tightlist
  \item
    PolNet-PaCSS 2025, Harvard University, MA \hfill Aug 2025
  \item
    PolMeth 2025, Emory University, GA \hfill July 2025
  \end{itemize}
\item
  ``State Legislators' Misinformation and the Limits of LLMs' Evaluative
  Reasoning''

  \begin{itemize}
  \tightlist
  \item
    Information and Misinformation in Elections, California Institute of
    Technology, CA \hfill Jan 2025
  \end{itemize}
\item
  ``The Digitally Accountable Public Representation Database: Measuring
  Online Communication by Federal, State, and Local Oﬀicials''

  \begin{itemize}
  \tightlist
  \item
    (Large) Language Models in Social Science 2024, University of
    Pennsylvania, PA \hfill Sep 2024
  \item
    PolMeth 2024, University of California, CA \hfill July 2024
  \end{itemize}
\item
  ``Climate Clash: Fossil Fuel Influence, Public Opinion, and State
  Legislators' Online Discourse''

  \begin{itemize}
  \tightlist
  \item
    APSA 2024, University of Pennsylvania, PA \hfill Sep 2024
  \item
    Visions in Methodology 2024, Washington University in St.Louis, MO
    \hfill May 2024
  \end{itemize}
\item
  ``Understanding Asian Hate in State Legislatures: An Electoral
  Connection''

  \begin{itemize}
  \tightlist
  \item
    State Politics and Policy Conference 2024, University of Virginia,
    VA \hfill June 2024
  \end{itemize}
\item
  ``The Prevalence of Misinformation in U.S. State Legislators' Facebook
  Posts''

  \begin{itemize}
  \tightlist
  \item
    American Political Science Association Conference 2023, LA
    \hfill Sep 2023
  \end{itemize}
\item
  ``Dynamic Trust and States' Failure in Public Health: Evidence from
  Global Time Series Data''

  \begin{itemize}
  \tightlist
  \item
    American Political Science Association Conference 2023, LA
    \hfill Aug 2023
  \end{itemize}
\item
  ``The Prevalence of Misinformation in U.S. State Legislators' Facebook
  Posts''

  \begin{itemize}
  \tightlist
  \item
    State Politics and Policy Conference 2023, University of Pittsburgh,
    PA \hfill May 2023
  \end{itemize}
\item
  ``How Does Public Opinion Affect Climate Change Policies? Constructing
  Measures of Climate Change Public Concern and Testing Their Effects on
  Policy Outputs''

  \begin{itemize}
  \tightlist
  \item
    Political Economy and International Relation Workshop, PSU
    \hfill Mar 2023
  \end{itemize}
\item
  ``The Upsides and Downsides of Generalized Trust: The Mediating Effect
  of Democratic Institutions and Trust in Implementing Institutions''

  \begin{itemize}
  \tightlist
  \item
    Southern Political Science Association Conference \hfill Jan 2023
  \end{itemize}
\item
  ``Democracy, Public Support, and Measurement Uncertainty''

  \begin{itemize}
  \tightlist
  \item
    C-SoDA Brownbag Series \hfill Oct 2022
  \end{itemize}
\item
  ``Examining States' Public Health Failures by Measuring Trust Cross
  Countries and Over Time''

  \begin{itemize}
  \tightlist
  \item
    C-SoDA Kickoff Poster Presentation \hfill Sep 2022
  \end{itemize}
\item
  ``Dynamic Trust and States' Failure in Public Health: Evidence from a
  Global Time Series Data''

  \begin{itemize}
  \tightlist
  \item
    Midwest Political Science Association Conference \hfill Apr 2022
  \item
    Iowa Women Studying Politics (IWSP) Conference \hfill Feb 2022
  \end{itemize}
\item
  ``Policy Burden, Issue Salience, and COVID-19 Policy Adoption in
  China''

  \begin{itemize}
  \tightlist
  \item
    APSA Chinese Politics Mini-Conference \hfill Oct 2021
  \end{itemize}
\item
  ``Democracy, Public Support, and Measurement Uncertainty''

  \begin{itemize}
  \tightlist
  \item
    Joint Quantitative Political Science Conference for Asia and
    Australasia \hfill Jan 2021
  \end{itemize}
\item
  ``Policy Orientation and Diffusion in Responsive Governance: Responses
  to the Chinese 2018 Vaccine Scandal.''

  \begin{itemize}
  \tightlist
  \item
    Association of Chinese Political Studies Annual Meeting \hfill Nov
    2020
  \end{itemize}
\item
  ``Who is Influencing Public Opinion during a Public Health Crisis on
  Social Media in China?''

  \begin{itemize}
  \tightlist
  \item
    Southern Political Science Association Conference \hfill  Jan 2020
  \end{itemize}
\end{itemize}

\section{TEACHING EXPERIENCE}\label{teaching-experience}

\begin{itemize}
\tightlist
\item
  \textbf{Invited Talk and Guest Lecture}

  \begin{itemize}
  \tightlist
  \item
    \textbf{Guest Speaker, Penn State University}
  \item
    Social Science Research Institute Open House \hfill Fall 2025

    \begin{itemize}
    \tightlist
    \item
      Hands-On with AI: Evaluating and Applying Models for Social
      Science Data
    \end{itemize}
  \item
    \textbf{Guest Speaker, Penn State University}
  \item
    Social Science Research Institute Open House (Open to Faculty
    Members in SSRI) \hfill Spring 2025

    \begin{itemize}
    \tightlist
    \item
      How to Navigate High Performance Computing
    \end{itemize}
  \item
    \textbf{Guest Lecturer, Penn State University}
  \item
    Approaches and Issues in Big Social Data (Graduate Level)
    \hfill Spring 2025

    \begin{itemize}
    \tightlist
    \item
      GenAI vs.~Human Fact-Checkers: Accurate Ratings, Flawed Rationales
    \end{itemize}
  \item
    \textbf{Guest Lecturer, University of Massachusetts Amherst}
  \item
    Data Analytics and Computational Social Science (Graduate Level)
    \hfill Fall 2024

    \begin{itemize}
    \tightlist
    \item
      LLMs in social science
    \end{itemize}
  \item
    \textbf{Guest Speaker, Xi'an Jiaotong University, China}
  \item
    Summer Speaker Series (Graduate Level) \hfill Summer 2023

    \begin{itemize}
    \tightlist
    \item
      Latent Variable Measurements
    \end{itemize}
  \item
    \textbf{Guest Lecturer, Penn State University}
  \item
    Approaches and Issues in Big Social Data (Graduate Level)
    \hfill Spring 2023

    \begin{itemize}
    \tightlist
    \item
      Measurement
    \end{itemize}
  \item
    \textbf{Guest Lecturer, University of Iowa}
  \item
    Advanced Methods Seminar (Graduate Level) \hfill Fall 2021

    \begin{itemize}
    \tightlist
    \item
      Machine Learning
    \end{itemize}
  \item
    Analyzing Political Data (Undergraduate Level) \hfill Spring 2021

    \begin{itemize}
    \tightlist
    \item
      P-Value \& Multiple Regression
    \end{itemize}
  \item
    Public Opinion

    \begin{itemize}
    \tightlist
    \item
      Public Opinion and Democracy \hfill Fall 2021
    \end{itemize}
  \item
    National Security Policy

    \begin{itemize}
    \tightlist
    \item
      Cyber Security \hfill March 2020
    \end{itemize}
  \item
    \textbf{Workshop, East China Normal University, Shanghai}
  \item
    Introduction to Python (Graduate Level) \hfill Dec 2020

    \begin{itemize}
    \tightlist
    \item
      Web scraping, social media data wrangling and analysis
    \end{itemize}
  \end{itemize}
\item
  \textbf{Method Courses}

  \begin{itemize}
  \tightlist
  \item
    \textbf{Instructor, Penn State University}
  \item
    C-SoDA Research Practicum: AI and Multimodal data (Undergraduate
    Level) \hfill Spring 2026
  \item
    \textbf{Instructor, Penn State University}
  \item
    C-SoDA Research Practicum: AI and Governance (Undergraduate Level)
    \hfill Fall 2025
  \item
    \textbf{Instructor, Penn State University}
  \item
    PLSC 10: Scientific Study of Politics (Undergraduate Level)
    \hfill Fall 2024
  \item
    Instructor, Penn State University
  \item
    PLSC 308: Introduction to Political Research (Undergraduate Level)
    \hfill Spring 2024
  \item
    Instructor, Penn State University
  \item
    SoDA 308: Research Design for Social Data Analytics (Undergraduate
    Level) \hfill Fall 2023
  \item
    \textbf{Independent Instructor, University of Iowa}
  \item
    Hawkeye Poll (Undergraduate Level) \hfill Spring 2022
  \item
    Guided students to design survey questions on both national and
    local politics, carry out telephone interviews,analyze and interpret
    data, and write release press and analytical papers.
  \item
    \textbf{Teaching Assistant, University of Michigan}
  \item
    Bayesian Modeling for the Social Sciences II: Advanced Topics, ICPSR
    Program, \hfill Summer 2021
  \item
    Graded students' assignments with detailed comments and offered
    one-on-one consultations on students' individual projects.
  \end{itemize}
\item
  \textbf{Comparative Politics and American Politics Courses}

  \begin{itemize}
  \tightlist
  \item
    Teaching Assistant, University of Iowa

    \begin{itemize}
    \tightlist
    \item
      Introduction to Political Behavior \hfill Fall 2019
    \item
      Introduction to Comparative Politics \hfill Fall 2018, Spring 2019
    \item
      The Presidency \hfill Fall 2017
    \item
      Introduction to Comparative Politics (Online Course) \hfill Summer
      2018, 2019
    \end{itemize}
  \end{itemize}
\end{itemize}

\section{EXTERNAL AND CAMPUS SERVICE}\label{external-and-campus-service}

\begin{itemize}
\tightlist
\item
  \textbf{Member}: American Political Science Association (sections on
  Political Methodology), Midwest Political Science Association, and
  Southern Political Science Association
\item
  \textbf{Reviewer}: American Political Science Review, American Journal
  of Political Science, British Journal of Political Science, Research
  and Politics, The International Conference on Weblogs and Social Media
  (ICWSM), International World Wide Web Conference 2025 (WWW2025),
  International World Wide Web Conference 2026 (WWW2026), Humanities and
  Social Sciences Communications, Public Opinion Quarterly, Asian
  Survey, International Journal of Public Opinion Research,
  International Journal of Comparative Sociology.
\item
  \textbf{Seed Grant Reviewer (``Analytical and Social AI'' program)}:
  Social Science Research Institute. Pennsylvania State University
  \hfill 2026
\item
  \textbf{AI Panel Facilitator}: 2026 Data Summit. Pennsylvania State
  University \hfill 2026
\item
  \textbf{Seed Grant Reviewer}: Center for Social Data Analytics.
  Pennsylvania State University \hfill 2022, 2023,2024,2025,2026
\item
  \textbf{POLMETH Mailing List Editor}: The Society for Political
  Methodology. \hfill 2024 -
\item
  \textbf{Planning Committee Member}: 16th Postdoctoral Research
  Symposium. Pennsylvania State University \hfill2023
\item
  \textbf{Committee Member}: Postdoctoral Scholar Committee. College of
  the Liberal Arts, Pennsylvania State University \hfill 2022
\item
  \textbf{iPeer Mentor}: iPeer Mentorship Program. International Student
  and Scholar Services, University of Iowa \hfill 2021
\item
  \textbf{Discussant}: Government Transparency in China. Midwest
  Political Science Association Annual Meeting \hfill Apr 2021
\item
  \textbf{Session Chair and Discussant}:Time and Space. Political
  Science Methodology Conference for Asia and Australasia \hfill  Jan
  2021
\item
  \textbf{Co-Host}:
  \href{https://clas.uiowa.edu/polisci/Shambaugh-2020Caucus}{\emph{2020
  Iowa Caucus Conference}}. University of Iowa \hfill Feb 2020
\item
  \textbf{Session Chair}: Understanding Polarization, COVID \&
  Computation and Social Media \& Politics. Politics and Computational
  Social Science and Political Networks \hfill Aug 2020
\item
  \textbf{Discussant}: Chinese Politics. Southern Political Science
  Association Conference \hfill Jan 2020
\end{itemize}

\section{AWARDS \& HONORS}\label{awards-honors}

\begin{itemize}
\tightlist
\item
  Nominated to Global Student Awards, University of Iowa \hfill Fall
  2021
\item
  Finalist for annual ``Thesis Challenge,'' University of Iowa
  \hfill Fall 2021
\item
  Graduate Post-Comp Research Fellowship (\$10,500), University of Iowa
  \hfill Fall 2021
\item
  Graduate College Summer Fellowship (\$5,000), University of Iowa
  \hfill Summer 2021
\item
  Department Research Grant (\$1,000), University of Iowa \hfill Spring
  2020
\item
  GSS Travel Funds (\$1,000), University of Iowa \hfill Spring 2020
\item
  Department Research Grant (\$300), University of Iowa \hfill Spring
  2019
\item
  Center for Asian and Pacific Studies Graduate Travel Grant (\$500),
  University of Iowa \hfill Fall 2019
\item
  Department Summer Training Grant (\$2400), University of Iowa
  \hfill Summer 2018
\end{itemize}

\section{ADDITIONAL TRAINING AND
SKILLS}\label{additional-training-and-skills}

\begin{itemize}
\tightlist
\item
  \textbf{Courses Taken in Graduate School}

  \begin{itemize}
  \tightlist
  \item
    \textbf{Methodology and Quantitative Analysis}: Introductory,
    Intermediate, and Advanced Methodology; Modeling Time and Space;
    Factor Analysis and Structural Equation Models
  \item
    \textbf{Computational and Data Science Methods}: Computational
    Methods for Comparative Politics; Text as Data; Introduction to
    Informatics; Network Analysis; Bayesian Analysis, Database
    Management
  \end{itemize}
\item
  \textbf{Training}

  \begin{itemize}
  \tightlist
  \item
    Summer Institutes in Computational Social Science, Rutgers, NJ
    \hfill2024
  \end{itemize}
\item
  \textbf{Certificate}

  \begin{itemize}
  \tightlist
  \item
    Certificate in Informatics, The University of Iowa, U.S.A.
    \hfill 2021

    \begin{itemize}
    \tightlist
    \item
      Programming in Python, Java, and SQL.
    \end{itemize}
  \item
    ICPSR, University of Michigan, Ann Arbor, MI \hfill 2018

    \begin{itemize}
    \tightlist
    \item
      Causal Inference for the Social Sciences \& Multilevel Models II:
      Advanced Topics.
    \end{itemize}
  \end{itemize}
\item
  \textbf{Skills}

  \begin{itemize}
  \tightlist
  \item
    Analysis \& Programming: R, Python, SQL, Stata, Stan, JAGS, Mplus,
    Java.
  \item
    Application: LaTeX, Markdown, Git(GitHub).
  \item
    Language: English, Chinese (Mandarin)
  \end{itemize}
\end{itemize}

\section{REFERENCES}\label{references}

\begin{itemize}
\tightlist
\item
  \textbf{Frederick Solt}, \textbf{Ph.D} \hfill \textbf{Bruce A.
  Desmarais}, \textbf{Ph.D}
\item
  \href{mailto:frederick-solt@uiowa.edu}{\nolinkurl{frederick-solt@uiowa.edu}};
  (319)335-2340
  \hfill  \href{mailto:bdesmarais@psu.edu}{\nolinkurl{bdesmarais@psu.edu}};
  (814) 863-1595,
\item
  Professor, University of Iowa \hfill  Professor, Penn State University
\item
  \textbf{Xun Cao}, \textbf{Ph.D} \hfill \textbf{Bryce Dietrich},
  \textbf{Ph.D}
\item
  \href{mailto:xuc11@psu.edu}{\nolinkurl{xuc11@psu.edu}}; (814) 865-8749
  \hfill  \href{mailto:bjdietri@purdue.edu}{\nolinkurl{bjdietri@purdue.edu}};
  (765) 494-4161
\item
  Professor, Penn State University \hfill Associate Professor, Purdue
  University
\item
  \textbf{Elizabeth J. Menninga}, \textbf{Ph.D}
\item
  \href{mailto:elizabeth-menninga@uiowa.edu}{\nolinkurl{elizabeth-menninga@uiowa.edu}};
  (319) 335-3835
\item
  Associate Professor, University of Iowa
\end{itemize}
	
			\end{document}